UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-03-17 paper/paper.tex
small refactorings
updates to Design: Intersection points

\documentclass[]{final_report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{csvsimple}

%%%%%%%%%%%%%%%%%%%%%%
%%% Project details
%%%%%%%%%%%%%%%%%%%%%%
\def\studentname{Kamil Smuga}
\def\projecttitle{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}
\def\supervisorname{Liam Murphy}
\def\moderatorname{Christina Thorpe}

@@

\maketitle
\tableofcontents\pdfbookmark[0]{Table of Contents}{toc}\newpage

%%%%%%%%%%%%%%%%%%%%%%
%%% ABSTRACT 
%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%\section{Thesis statement}
%\emph{ /* Based on~\cite{proofByConstruction} I have to provide a statement that will be proven by construction. Is it a valid approach? */} \par

%To have a grasp on 'how optimal my infrastructure provisioning is' one should gather VM usage data, split and calculate optimality KPIs

%To answer price optimality questions asked by IaaS customer, one should split and model usage data and run optimality KPIs based on

\section{Structure of the Document}

\textbf{Background}. This section will outline the background information related to IaaS consumer challenges related to understanding the whole picture for price optimality of rented infrastructure. \par
\textbf{Design}. This section explains design and environment conditions for the algorithm to be useful. \par
\textbf{Implementation}. This sections explains algorithm implementation details and data analytics software that was used - Apache Spark~\cite{spark}. \par
\textbf{Evaluation}. The proposed algorithmic approach is applied on Google Trace data~\cite{googleTrace}. \par
\textbf{Conclusion and Further Work}. The completed data analysis is discussed. Further work related to algorithm improvements, automation and lessons learned are presented.

@@

Cost per hour represents a total cost of running a single machine divided by number of hours in calendar year. Aggregated cost is relatively easy to calculate in rented, virtualized environments. IaaS providers usually charge an X amount per hour. It might vary based on total uptime per month or pricing scheme. This number will be considered as a partial cost per hour and defined as \textit{pcph}. \par
Cost of running of physical hardware is less straightforward to calculate as it includes: power consumption, operations, hardware replacements cost, data center related costs and many others that may vary based on individual cases. Although more troublesome to calculate, cost per hour per host for physical infrastructure is possible to calculate. \par
Cost per hour will be defined as \textit{cph}. It includes upfront cost and IaaS provider per hour charges. It is defined as a function of hours of utilization per day.

@@

\subsection{Intersection points between pricing schemes}
\emph{/* How to find points when one pricing scheme becomes */}

@@

\section{Calculate cost per hour for a given pricing scheme}
Results for ccs2.xlarge based on data published for AWS~\cite{AWS:2014} \par
\csvautotabular{out}
\section{Calculate intersection points to find out the best pricing scheme for a number of hours/day utilization}
\includegraphics[width=\linewidth]{cph}
\section{Collect VM usage data}
\section{Group usage metrics by machine}
\section{Calculate number of hours/day, distance from optimality points, CPU and memory utilization}
\section{Suggest changes to the least optimal VMs considering SLAs based on CPU and memory utilization}

@@

\chapter{Conclusion and Further Work}

>>>>

\documentclass[]{final_report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{csvsimple}
\usepackage{float}

%%%%%%%%%%%%%%%%%%%%%%
%%% Project details
%%%%%%%%%%%%%%%%%%%%%%
\def\studentname{Kamil Smuga}
\def\projecttitle{An approach for Continuous Capacity Planning in Cloud Environments with an Uptime-based Pricing Model}
\def\supervisorname{Prof. Liam Murphy}
\def\moderatorname{Christina Thorpe}

@@

\maketitle
\tableofcontents\pdfbookmark[0]{Table of Contents}{toc}\newpage
\listoffigures\newpage
\par{\textbf{List of tables}}

%%%%
%The most important parts of your thesis are: abstract, introduction, conclusion and
%references. These are what get read first and make that vital initial impression.
%%%
%%%
%One of first things your examiners will look at is your literature review. If they see a
%good number of journal papers, a swathe of conference papers, a few recent workshop
%papers and not too many web sites, they’ll already be impressed.
%%%
%%%%%%%%%%%%%%%%%%%%%%
%%% ABSTRACT 
%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Description of the problem}

\section{Motivation for solving the problem}

@@

\section{Related work}

\section{Challenges}

\section{Description of methodology}
Modelling and experimentation

\section{Structure of the Thesis}
\textbf{Background}. This section will outline the background information related to IaaS consumer challenges related to understanding the whole picture for price optimality of rented infrastructure. \par
\textbf{Design}. This section explains design and environment conditions for the algorithm to be useful. \par
\textbf{Implementation}. This sections explains algorithm implementation details and data analytics software that was used - Apache Spark~\cite{spark}. \par
\textbf{Evaluation}. The proposed algorithmic approach is applied on Google Trace data~\cite{googleTrace}. \par
\textbf{Conclusion and Further Work}. The completed data analysis is discussed. Further work related to algorithm improvements, automation and lessons learned are presented.

@@

Cost per hour represents a total cost of running a single machine divided by number of hours in calendar year. Aggregated cost is relatively easy to calculate in rented, virtualised environments. IaaS providers usually charge an X amount per hour. It might vary based on total uptime per month or pricing scheme. This number will be considered as a partial cost per hour and defined as \textit{pcph}. \par
Cost of running of physical hardware is less straightforward to calculate as it includes: power consumption, operations, hardware replacements cost, data center related costs and many others that may vary based on individual cases. Although more troublesome to calculate, cost per hour per host for physical infrastructure is possible to calculate. \par
Cost per hour will be defined as \textit{cph}. It includes upfront cost and IaaS provider per hour charges. It is defined as a function of hours of utilization per day.

@@

\subsection{Intersection points between pricing schemes}

Cost per hour is calculated for each of available pricing schemes. Single result represents a matrix of hours per day and \textit{cph}. Graphical representation of results will produce a graph similar to Figure~\ref{fig:cc2_8xlarge}. Pricing trends are visible. Price drops exponentially for around first 5 hours of usage and almost stabilizes afterwards. Light is the cheapest option for around 15 hours per day usage. This is better visible on Figure~\ref{fig:cph_cc2_8xlarge_zoom}. After 15 hours, it is better to invest in Heavy utilization scheme. This is a point that will be called an intersection point between 2 pricing schemes and referred as \textit{ip(scheme1, scheme2)}. In this example, we can calculate that for cc2.8xlarge instance \textit{ip(light, heavy) = 16}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{figures/cc2_8xlarge}
	\caption{\textit{cph} results for Amazon AWS cc2.8xlarge reserved instance for 1 year~\cite{AWS:2014}}
	\label{fig:cc2_8xlarge}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{figures/cph_cc2_8xlarge_zoom}
	\caption{Zoomed \textit{cph} results for Amazon AWS cc2.8xlarge reserved instance for 1 year~\cite{AWS:2014}}
	\label{fig:cph_cc2_8xlarge_zoom}
\end{figure}

@@

\section{Methodology and setup description}

\section{Algorithm walkthrough}
\subsection{Calculate cost per hour for a given pricing scheme}
Results for ccs2.xlarge based on data published for AWS~\cite{AWS:2014} \par
\csvautotabular{out}
\subsection{Calculate intersection points to find out the best pricing scheme for a number of hours/day utilization}
%\includegraphics[width=\linewidth]{cph}
\subsection{Collect VM usage data}
\subsection{Group usage metrics by machine}
\subsection{Calculate number of hours/day, distance from optimality points, CPU and memory utilization}
\subsection{Suggest changes to the least optimal VMs considering SLAs based on CPU and memory utilization}

\section{Summary}

@@

\chapter{Conclusion and Future Work}
